---
title: "gg_venn"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gg_venn}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(ggvenn)
```

```{r include=FALSE}
library(tidyverse)
```

## Quick Start

### Input

ggvenn was created to draw simple venn diagrams using ggplot. Since the resulting plots are grid based graphics, the plots can be further customized using traditional ggplot methods.

The `gg_venn()` function takes a named list as an input and calculates the overlap among the lists and plots an appropriate venn diagram. Currently up to a 4-way venn diagram is supported. 

```{r}
numbers <- list(evens = c(2,4,6), primes = c(2,3,5,7),
                odds = c(1,3,5,7), ordered = c(1,2,3,4,5,6,7,8))
```

```{r two_way, fig.height=6, fig.width=8}
gg_venn(numbers[c('evens','primes')]) 
```


```{r three_way, eval=FALSE, include=FALSE, fig.height=6, fig.width=8}
gg_venn(numbers[c('evens','primes', 'odds')]) 

```

By default, the size of the circles will ve scaled to represent the lengths of each item in the list for 2 and 3 way comparisons 


```{r four_way, fig.height=6, fig.width=8}
gg_venn(numbers) 
```

### Customization

#### Label Colors
The color of the labels can be changed by passing a color or vector of colors of appropriate length to the **label.col** argument. 

|----|----|
|2 way| 3 |
|3 way| x |
|4 way| 15 |

```{r fig.height=6, fig.width=8}
gg_venn(numbers, label.col = 'red')
```

#### Label sizes
The size of the labels can be set using the  **label.size** argument. 

```{r fig.height=6, fig.width=8}
gg_venn(numbers, label.size = 10)
```

##### ggplot customizations
###### Adjusting venn colors
```{r fig.height=6, fig.width=8}
gg_venn(numbers) +
  scale_fill_manual(values = c('red','grey','blue','green'))
```

###### Add labels to venns 
The annotate function can be used to add labels to the individual circles of the venn diagrams. x and y coordinates can be determined by adjusting the plot theme to show the x and y axis

```{r fig.height=6, fig.width=8}
gg_venn(numbers[c('evens','primes')]) +
  theme_grey()+
  annotate("text",
           x =  c(-.75, 1),
           y =   c(1.25,1),
           label =  c('Evens', 'Odds'),
           size = 10)
           
 
```